### 2022-08-31 poster_eccb22_barcelona/poster_eccb22_barcelona.tex
ENH improved

	%\newcounter{table}
	\setcounter{table}{1}
	\newcommand{\mycaptiontab}[1]{
	  \vspace{0.25cm}
	  \begin{quote}%\centering
	    {{\bf Table \arabic{table}:} #1}
	  \end{quote}
	  \vspace{0.5cm}
	  \stepcounter{figure}
	}

@@

	\begin{center}
	%\begin{pcolumn}{1}
	\pbox{0.98\textwidth}{}{linewidth=2mm,framearc=0.3,linecolor=lightblue,fillstyle=gradient,gradangle=0,gradbegin=white,gradend=whiteblue,gradmidpoint=1.0,framesep=0.25em}{
	\begin{minipage}[c][10cm][c]{0.1\textwidth}
	  \begin{center}
	    \includegraphics[width=12cm,angle=0]{img_tmp/logo_sciences.eps}
	  \end{center}
	\end{minipage}
	\begin{minipage}[c][9cm][c]{0.7\textwidth}
	  \begin{center}
	%Microarray analysis of chicken and mouse presomitic mesoderm along the posterior-anterior axisS
	%    {\sc \Huge Microarray analysis of chicken and mouse}\\[4.mm]
	%    {\sc \Huge presomitic mesoderm along the posterior-anterior axis}\\[2.mm]
	%\vspace{1cm}
	    { \fonttitle{Analysis of gene regulatory properties} }\\[4.mm]
	    { \fonttitle{underlying trait pleiotropy} }\\[2.mm]
	    \huge Aitor Gonz\'alez$^*$\\[2.mm]
	    \large TAGC Laboratory, Aix-Marseille Univ, INSERM UMR1090, 13288 Marseille, France\\[2.mm]
	    \large $^*$Email: aitor.gonzalez@univ-amu.fr
	  \end{center}
	  \end{minipage}
	\begin{minipage}[c][10cm][c]{0.1\textwidth}
	  \begin{center}
	    \includegraphics[width=12cm,angle=0]{img_tmp/logo_tagc_400x230_centered_1.eps}
	    \includegraphics[width=12cm,angle=0]{img_tmp/logo_tagc_400x230_centered_1.eps}
	  \end{center}
	\end{minipage}
	} % end pbox
	%\end{pcolumn}
	\end{center}

@@

	\begin{enumerate}
	\item Genome-wide association studies (GWAS) map genotypes to traits.
	\item The IEU OpenGWAS project is a database of GWAS:\\ \url{https://gwas.mrcieu.ac.uk}
	\item The large number of available GWAS have allowed to define pleiotropic regions in the genome (\citep{2019.Posthuma.Watanabe}).
	\item Most GWAS loci are non-coding but the gene regulatory basis of pleiotropy is well understood.
	\item Expression quantitative trait loci (eQTL) map genotypes to expression phenotypes.
	\item The EBI eQTL Catalogue is a database of uniformely processed eQTLs:\\ \url{https://www.ebi.ac.uk/eqtl}
	\item The R package coloc performs colocalization tests between genetic traits:\\ \url{https://CRAN.R-project.org/package=coloc}
	\end{enumerate}

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% FIGURE 1
	\begin{minipage}{1\columnwidth}
	    \begin{center}
		    \begin{minipage}{0.32\columnwidth} 
			    \includegraphics[width=\columnwidth]{img_tmp/pltbar_x_per_variant_etissue_y_egene.eps}
		    \end{minipage}
		    \begin{minipage}{0.32\columnwidth} 
			    \includegraphics[width=\columnwidth]{img_tmp/pltbar_x_per_variant_egene_y_etissue.eps}
		    \end{minipage}
		    \begin{minipage}{0.32\columnwidth} 
			    \includegraphics[width=\columnwidth]{img_tmp/pltbar_x_per_variant_egene_etissue_y_gwas.eps}
		    \end{minipage}
		    \mycaptionfig{Count of eGenes per variant-tissue (\textbf{Left}), eTissues per variant-eGene (\textbf{Center}) and GWAS categories per variant-eGene-eTissue (\textbf{Right}).}
	    \end{center}
	\end{minipage}

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% FIGURE 2 VEP
	\begin{minipage}{1\columnwidth}
	    \begin{center}
		    \begin{minipage}{0.32\columnwidth} 
			    \includegraphics[width=\columnwidth]{img_tmp/missense_variant.eps}
		    \end{minipage}
		    \begin{minipage}{0.32\columnwidth} 
			    \includegraphics[width=\columnwidth]{img_tmp/splice_region_variant.eps}
		    \end{minipage}
		    \begin{minipage}{0.32\columnwidth} 
			    \includegraphics[width=\columnwidth]{img_tmp/3_prime_UTR_variant.eps}
		    \end{minipage}
		    \mycaptionfig{Variant effect predictor (VEP) analysis as a function of the number of GWAS catategory number for three different consequences: Missense variant (Left), splice region variant (Center) and 3’ UTR variant (Right)}
	    \end{center}
	\end{minipage}

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% FIGURE 2
	\begin{minipage}{1\columnwidth}
	    \begin{center}
		    \begin{center}
			    \begin{minipage}{0.35\columnwidth} 
				    \includegraphics[width=\columnwidth]{img_tmp/bxplt_remaptf_per_rsid_flank_0.eps}
			    \end{minipage}
			    \begin{minipage}{0.6\columnwidth} 
			    \mycaptionfig{Binding count of transcription factors in the region surrounding pleiotropic variants (Radius 50 bp) as a function of the GWAS category count. }
			    \end{minipage}
		    \end{center}
	    \end{center}
	\end{minipage}

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% FIGURE 3
	\begin{minipage}{1\columnwidth}
	    \begin{center}
		    \begin{minipage}{1\columnwidth} 
			    \includegraphics[width=\columnwidth]{img_tmp/graphical_summary.eps}
		    \end{minipage}
		    \mycaptionfig{Model of regulatory variant pleiotropy. I have investigated
	three possible mechanisms of pleiotropy. Left, Pleiotropic variants have more
	eGenes that result in more functions and more phenotypes. This might arise
	from an enrichment of pleiotropic variants in splicing or 3’ UTR regions.
	Center, I have also found that eGenes of pleiotropic variants are active
	in more etissues which result in more GWAS phenotypes. This might be
	explained from variants being bound by more transcription factors. Left
	Triplets of variant-eGene-eTissues are associated with more GWAS pheno-
	types, which directly affect the number of GWAS phenotypes. I have found
	that this might be explained by an enrichment of missense alleles.}
	    \end{center}
	\end{minipage}

@@

	\begin{itemize}
	\fontbody

	\item A pipeline to colocalize eQTLs and GWAS variantsWe present a new method to learn a supervised model of associated SNPs based on regulatory features (Fig. 1).
	\item We present a new method to learn a supervised model of associated SNPs based on regulatory features (Fig. 1).

	\end{itemize}

>>>>

	%\newcounter{table}
	\setcounter{table}{1}
	\newcommand{\mycaptiontab}[1]{
	  \vspace{0.25cm}
	  \begin{quote}%\centering
	    {{\bf Table \arabic{table}:} #1}
	  \end{quote}
	  \vspace{0.5cm}
	  \stepcounter{table}
	}

@@

	\begin{center}
	%\begin{pcolumn}{1}
	\pbox{0.98\textwidth}{}{linewidth=2mm,framearc=0.3,linecolor=lightblue,fillstyle=gradient,gradangle=0,gradbegin=white,gradend=whiteblue,gradmidpoint=1.0,framesep=0.25em}{
	\begin{minipage}[c][10cm][c]{0.1\textwidth}
	  \begin{center}
	    \includegraphics[width=12cm,angle=0]{img_tmp/tagc_logo.eps}
	    \includegraphics[width=12cm,angle=0]{img_tmp/inserm.eps}
	  \end{center}
	\end{minipage}
	\begin{minipage}[c][9cm][c]{0.7\textwidth}
	  \begin{center}
	%Microarray analysis of chicken and mouse presomitic mesoderm along the posterior-anterior axisS
	%    {\sc \Huge Microarray analysis of chicken and mouse}\\[4.mm]
	%    {\sc \Huge presomitic mesoderm along the posterior-anterior axis}\\[2.mm]
	%\vspace{1cm}
	    { \fonttitle{Analysis of gene regulatory properties} }\\[4.mm]
	    { \fonttitle{underlying trait pleiotropy} }\\[2.mm]
	    \huge Aitor Gonz\'alez$^*$\\[2.mm]
	    \large TAGC Laboratory, Aix-Marseille Univ, INSERM UMR1090, 13288 Marseille, France\\[2.mm]
	    \large $^*$Email: aitor.gonzalez@univ-amu.fr
	  \end{center}
	  \end{minipage}
	\begin{minipage}[c][10cm][c]{0.1\textwidth}
	    \includegraphics[width=12cm,angle=0]{img_tmp/DIRCOM-Logo-FSS.eps}
	  \begin{center}
	  \end{center}
	\end{minipage}
	} % end pbox
	%\end{pcolumn}
	\end{center}

@@

	\begin{enumerate}
	\item Genome-wide association studies (GWAS) map genotypes to traits.
	\item Here we use this GWAS database: The IEU OpenGWAS project\\ \url{https://gwas.mrcieu.ac.uk}
	\item The large number of available GWAS have allowed to define pleiotropic regions in the genome (\citep{2019.Posthuma.Watanabe}).
	\item Most GWAS loci are non-coding but the gene regulatory basis of pleiotropy is not well understood.
	\item Expression quantitative trait loci (eQTL) map genotypes to expression phenotypes.
	\item Here we use this eQTL database: The EBI eQTL Catalogue\\ \url{https://www.ebi.ac.uk/eqtl}
	\item The R package coloc performs colocalization tests between genetic traits:\\ \url{https://CRAN.R-project.org/package=coloc}
	\end{enumerate}

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% FIGURE 2 downstream regulation
	\begin{minipage}{1\columnwidth}
	    \begin{center}
		    \begin{minipage}{\columnwidth} 
\includegraphics[width=\textwidth]{img_tmp/david_pleio_3.eps}
\includegraphics[width=\textwidth]{img_tmp/david_pleio_2.eps}
		    \end{minipage}
		    \mycaptionfig{Gene ontology analysis of eGenes of variants associated to three (\textbf{a}) and two (\textbf{b}) GWAS categories compared to eGenes of variants associated to one GWAS category.}
	    \end{center}
	\end{minipage}

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% FIGURE 1 VEP
	\begin{minipage}{1\columnwidth}
	    \begin{center}
		    \begin{minipage}{0.32\columnwidth} 
			    \includegraphics[width=\columnwidth]{img_tmp/missense_variant.eps}
		    \end{minipage}
		    \begin{minipage}{0.32\columnwidth} 
			    \includegraphics[width=\columnwidth]{img_tmp/splice_region_variant.eps}
		    \end{minipage}
		    \begin{minipage}{0.32\columnwidth} 
			    \includegraphics[width=\columnwidth]{img_tmp/3_prime_UTR_variant.eps}
		    \end{minipage}
		    \mycaptionfig{Variant effect predictor (VEP) analysis as a function of the number of GWAS catategory number for three different consequences: Missense variant (Left), splice region variant (Center) and 3’ UTR variant (Right)}
	    \end{center}
	\end{minipage}

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% FIGURE 2 downstream regulation
	\begin{minipage}{1\columnwidth}
	    \begin{center}
		    \begin{minipage}{0.32\columnwidth} 
			    \includegraphics[width=\columnwidth]{img_tmp/pltbar_x_per_variant_etissue_y_egene.eps}
		    \end{minipage}
		    \begin{minipage}{0.32\columnwidth} 
			    \includegraphics[width=\columnwidth]{img_tmp/pltbar_x_per_variant_egene_y_etissue.eps}
		    \end{minipage}
		    \begin{minipage}{0.32\columnwidth} 
			    \includegraphics[width=\columnwidth]{img_tmp/pltbar_x_per_variant_egene_etissue_y_gwas.eps}
		    \end{minipage}
		    \mycaptionfig{Count of eGenes per variant-tissue (\textbf{Left}), eTissues per variant-eGene (\textbf{Center}) and GWAS categories per variant-eGene-eTissue (\textbf{Right}).}
	    \end{center}
	\end{minipage}

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% FIGURE 3 TFs
	\begin{minipage}{1\columnwidth}
	    \begin{center}
		    \begin{center}
			    \begin{minipage}{0.35\columnwidth} 
				    \includegraphics[width=\columnwidth]{img_tmp/bxplt_remaptf_per_rsid_flank_0.eps}
			    \end{minipage}
			    \begin{minipage}{0.6\columnwidth} 
			    \mycaptionfig{Binding count of transcription factors in the region surrounding pleiotropic variants (Radius 50 bp) as a function of the GWAS category count. }
			    \end{minipage}
		    \end{center}
	    \end{center}
	\end{minipage}

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% FIGURE 4 Model
	\begin{minipage}{1\columnwidth}
	    \begin{center}
		    \begin{minipage}{1\columnwidth} 
			    \includegraphics[width=\columnwidth]{img_tmp/graphical_summary.eps}
		    \end{minipage}
		    \mycaptionfig{Model of regulatory variant pleiotropy. I have investigated
	three possible mechanisms of pleiotropy. Left, Pleiotropic variants have more
	eGenes that result in more functions and more phenotypes. This might arise
	from an enrichment of pleiotropic variants in splicing or 3’ UTR regions.
	Center, I have also found that eGenes of pleiotropic variants are active
	in more etissues which result in more GWAS phenotypes. This might be
	explained from variants being bound by more transcription factors. Left
	Triplets of variant-eGene-eTissues are associated with more GWAS pheno-
	types, which directly affect the number of GWAS phenotypes. I have found
	that this might be explained by an enrichment of missense alleles.}
	    \end{center}
	\end{minipage}

@@

	\begin{itemize}	
	\item We have developed a pipeline of eQTL/GWAS colocalization (Fig. 1).
	\item These colocalization results are in an easy to use web site (Fig. 1).
	\item We have computed a list of pleiotropic eQTLs (Table 1).
	\item Pleiotropic variants are enriched in missense and splice region VEP effect consequences (Fig. 2).
	\item Pleiotropic eQTLs have more eGenes per variant-eTissue, are active in more eTissues per variant-eGene and are associated to more GWAS categories per variant-eGene-eTissue (Fig. 3).
	\item Pleiotropic variants bind transcription factors (Fig. 4).
	\item Model explaining the reason of pleiotropy for eQTLs (Fig. 5).
	\end{itemize}
